Hierarchical wrinkling in a confined permeable biogel

### 2015-04-24 fig_plis/article_SI.tex
fig:ripples plus que fig:growth

The primary, secondary and tertiary patterns follow the same path: the birth of an instability of wavelength $\lambda$ of growing amplitude until saturation. Throughout the whole process, $\lambda$ remains constant. This path is dynamic in essence. In Figure~\ref{fig:sideview}d, we thus report the velocity $v(t)$ of the wrinkles as it develops in the $z$-direction, see Supplementary Methods for the definition. We observe that the velocity peaks at different times corresponding to the syn\ae{}resis and the respective growths of the primary, secondary and tertiary patterns. We associate each growth with a characteristic time $\tau = e/v_\text{max}$. For example, in the present case the $\tau$ corresponding to the primary pattern is $\SI{123}{\second}$.

We do not observe coarsening of the patterns as in~\cite{Yoo2003}. We believe the wrinkling pattern is stable against coarsening because of the bending rigidity of the gel~\cite{LeGoff2014}. Indeed when the amplitude saturates the gel flattens against the walls and create sharp edges. To accommodate those sharp edges with finite bending rigidity, the flat part of the gel actually ripples, see Supplementary Figure~\ref{fig:growth}b. The ripples created by opposite sides of a same flat patch interfere, creating barriers against coarsening.

@@

\section*{Microstructure measurements}

@@

\section*{Characteristic time measurements}
\begin{figure}
	\includegraphics{growth}
	\caption{Growth of the instability. (a) Evolution of the peak-to-peak amplitude $A(t)$ in semi logarithmic scales. The black line is the best exponential fit with $\tau=\SI{90}{\second}$. (b) Evolution of the bottom profile of the gel from onset of instability (yellow) to contact to both walls (brown). The longitudinal size of the blister evolves in this regime. The thick black curve is the profile at much longer times and is at lower altitude due to swelling. The blister foot, highlighted by the orange vertical line, does not move after contact.}
	\label{fig:growth}
\end{figure}

@@

We note that when both measurements were available (as in Figure~\ref{fig:sideview}d of the main text and inset of Supplementary Figure~\ref{fig:growth}), the characteristic time $\tau$ obtained from the fit of the exponential growth of $A(t)$ is about $4A_\text{max}/v_\text{max}$, where $A_\text{max} = e-h$ is the amplitude when the gel comes in contact with both walls and $v_\text{max}$ is the maximum velocity of the gel. We use this approximation of $\tau$ for all our samples. This is consistent with the fact that the blister size ($\propto\lambda$) does not evolve after contact, see Supplementary Figure~\ref{fig:growth}, thus the kinetic wavelength is set when $A(t) = A_\text{max}$.

@@

\section*{Wavelength measurements}

@@

>>>>

The primary, secondary and tertiary patterns follow the same path: the birth of an instability of wavelength $\lambda$ of growing amplitude $A(t)$ until saturation, see Figure~\ref{fig:sideview}a. Throughout the whole process, $\lambda$ remains constant. This path is dynamic in essence. In Figure~\ref{fig:sideview}d, we thus report the velocity $v(t)$ of the wrinkles as it develops in the $z$-direction, see Supplementary Methods for the definition. We observe that the velocity peaks at different times corresponding to the syn\ae{}resis and the respective growths of the primary, secondary and tertiary patterns. We associate each growth with a characteristic time $\tau = A_\text{max}/v_\text{max}$. For example, in the present case the $\tau$ corresponding to the primary pattern is $\SI{123}{\second}$.

We do not observe coarsening of the patterns as in~\cite{Yoo2003}. We believe the wrinkling pattern is stable against coarsening because of the bending rigidity of the gel~\cite{LeGoff2014}. Indeed when the amplitude saturates the gel flattens against the walls and create sharp edges. To accommodate those sharp edges with finite bending rigidity, the flat part of the gel actually ripples, see Supplementary Figure~\ref{fig:ripples}. The ripples created by opposite sides of a same flat patch interfere, creating barriers against coarsening.

@@

\subsection*{Microstructure measurements}

@@

\subsection*{Characteristic time measurements}

@@

@@

\subsection*{Wavelength measurements}

@@

\begin{figure}
\includegraphics{ripples.pdf}
\caption{Evidence of the ripples generated by the junction to flat patches, see~\cite{LeGoff2014}. Position of the bottom surface of the gel in (a) 2D and (b) 1D. Only first ripple is visible, highlighted by orange rectangles. (c) Schematic view of the interference between ripples.}
\label{fig:ripples}
\end{figure}
